\subsection{Scope:}
\noindent This project focuses on enhancing search systems by refining user queries through advanced Natural Language Processing (NLP) techniques. The system aims to improve the accuracy and relevance of search results across both general and domain-specific applications by restructuring queries based on user context and intent.
\begin{enumerate}
    \item Refines user queries using NLP to produce more meaningful and context-aware search inputs.
    \item Enhances search performance for both general use cases and specialized domains like healthcare, education, or legal research.
    \item Uses modular components (e.g., preprocessing,keyword expansion) that can be independently extended or replaced.
    \item Designed for easy integration with existing search engines, knowledge bases, or recommendation systems.
    \item Can act as a middleware layer between users and different search platforms, improving relevance without modifying backend systems.
    \item Web-based architecture ensures accessibility across devices and environments.
    \item Offers potential for future expansion to support multiple languages and domain-specific adaptations.
\end{enumerate}

\newpage
\subsection{Limitations:}
\noindent While the system significantly improves query refinement, there are certain constraints related to model performance, domain adaptability, and system integration. These limitations help define the current operational boundaries of the project. following limitations:
\begin{enumerate}
    \item NLP model performance depends on the quality and coverage of the training data.
    \item Queries that are too vague or too short may not benefit significantly from refinement.
    \item Domain-specific accuracy requires fine-tuning with relevant datasets, which may not always be readily available.
    \item Integration with some closed or proprietary search engines may be technically or legally restricted.
    \item Real-time performance may degrade under high-volume or resource-constrained environments without further optimization.
    \item The system focuses on refining the input query only and does not alter the internal ranking mechanisms of the search engine.
\end{enumerate}
