\subsection{Frontend}
\begin{itemize}
    \item Built a responsive web interface using the \textbf{Nuxt.js} framework, leveraging server-side rendering for enhanced performance and SEO.
    \item Implemented modern UI design using \textbf{Tailwind CSS}, a utility-first CSS framework, ensuring consistent and efficient styling.
    \item Ensured cross-browser compatibility and mobile responsiveness by testing and optimizing the application across various devices and browsers.
\end{itemize}

\subsection{Backend}
\begin{itemize}
    \item Developed a robust API using the \textbf{Django} framework, creating a scalable backend architecture with Python.
    \item Created \textbf{RESTful endpoints} to enable efficient and structured data communication.
    \item Integrated an AI model for intelligent data processing, applying machine learning techniques to analyze and interpret user data.
\end{itemize}

\subsection{NLP Processing}
\begin{itemize}
    \item Implemented text preprocessing techniques including lowercasing, digit and punctuation removal, and stopword filtering.
    \item Applied tokenization and lemmatization using the \textbf{spaCy} library.
    \item Extracted part-of-speech-specific tokens, focusing on nouns and adjectives to identify high-quality keyword candidates.
    \item Performed noun phrase extraction using \texttt{spaCy}'s \texttt{noun\_chunks} for more context-rich keywords.
    \item Explored topic modeling using \textbf{Latent Dirichlet Allocation (LDA)} and tuned the number of topics by evaluating coherence scores.
    \item Compared multiple keyword extraction techniques, including \textbf{KeyBERT}, noun phrase extraction, and LDA-based topic modeling.
\end{itemize}

